Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-04 demystify.tex
updates

\section{Application Materials}

@@

\paragraph{Funding \S\ref{sec:funding}} You have more opportunities for funding, e.g., through government scholarships for US citizens and residents.  You can also apply to specific programs \emph{before} you start your PhD, e.g., NSF Graduate Research Fellowship Program (GRFP) and Hertz Foundation Fellowship.  These fellowships can be very competitive and will improve your admission chance if you get them.

@@

\paragraph{Standing out} There are very few domestic applications compared to international ones (i.e., domestic students are minority in the CS PhD application pool), and many US universities want to increase the number of domestic students in their programs.
That makes you stand out and can help your case.

>>>>

@@

\paragraph{Funding \S\ref{sec:funding}} You have more opportunities for funding, e.g., through government scholarships for US citizens and permanent residents.  You can also apply to specific programs \emph{before} you start your PhD, e.g., NSF Graduate Research Fellowship Program (GRFP) and Hertz Foundation Fellowship.  These fellowships can be very competitive and will improve your admission chance if you get them.

@@

\paragraph{Standing out} There are \emph{very few} domestic applications compared to international ones (i.e., domestic students are minority in the CS PhD application pool), and many US universities want to increase the number of domestic students in their programs (and as mentioned above, there are specific fellowships for domestic students).
That makes you stand out and can help your case.
